Founder allele effects for hotspot traits

### 2019-08-19 analysis/paper/preliminary/allele-effects-exploration.Rmd
deleted calculate_contrasts function.
defined 'ef' as list of lists
fixed calcs

>>>>

## Calculate all partitions & contrasts

```{r}
pp <- expand.grid(1:3, 
                  1:3,
                  1:3, 
                  1:3,
                  1:3, 
                  1:3,
                  1:3, 
                  1:3
                  )
effects_mat <- local_nonlocal_annot %>%
  ungroup() %>%
  select(cA:cH) %>%
  as.matrix()

```{r}
pp_tib <- pp %>%
  as_tibble()
effects_tib <- effects_mat %>%
  as_tibble()

ef <- pp_tib %>%
  apply(MARGIN = 1, 
        FUN = function(x){apply(X = effects_tib, 
                                MARGIN = 1, 
                                FUN = function(a, b = x){calc_contrast(grouping = b, effects = a)}
                                )})

ef %>%  apply(FUN = function(x) x[!is.na(x)], MARGIN = 1) %>% 
  lapply(FUN = function(x) bind_rows(x)) %>%
  purrr::map2(local_nonlocal_annot$symbol, .f = function(x,y){x %>% mutate(symbol = y)}) %>%
  bind_rows() %>%
  filter(contrast == "A_B") 
  summarise(v = var(value)) %>%
  arrange(desc(v))
```
